---
title: "Weight of Fish"
author: "Joel Calderin"
date: "Fall 2023`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(dplyr)
library(leaps)
fish = read.csv("Fish.csv")
```

# Predicting Fish Weight

Find the best model using two variables to predict perch, pike, and roach weight, and compare this to the best over-all model

## Perch
```{r}
Perch = filter(fish, Species == 'Perch')
```

## Best 2 Regressor Model 
```{r}
modelPerch = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = Perch)
summary(modelPerch)
```

## Best 2-Variable predictor is Height and Width

```{r}
best2Perch= lm(Weight ~ Height + Width, data = Perch)
summary(best2Perch)
```

### Best 2-Variable equation
Weight = -536 + 74.77 * Height + 69.62 * Width


## Pike
```{r}
Pike = filter(fish, Species == 'Pike')
```

### Best Two regressor model

```{r}
modelPike = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = Pike)
summary(modelPike)
```

## Best 2-Variable Predictor is Length1 and Length3

```{r}
best2Pike= lm(Weight ~ Length1 + Length3,  data = Pike)
summary(best2Pike)
```

## Best 2-Variable Equation

Weight= -1675.79 + -105.64 * Length1 + 141.25 * Length3

## Roach
```{r}
Roach = filter(fish, Species == 'Roach')
```


### Best Two regressor model
```{r}
modelRoach= regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = Roach)
summary(modelRoach)
```
 
## Best 2-Variable Predictor is Length3 and Width

```{r}
best2Roach= lm(Weight ~ Length3 + Width,  data = Roach)
summary(best2Roach)
```

## Best 2-Variable Equation

Weight= -319.118 + 8.278 * Length3 + 72.300 * Width


## Final Summary Statements

The best model using two variables to predict Perch weight is height and width. The equation is Weight = -536 + 74.77 * Height + 69.62 * Width.

The best model using two variables to predict Pike weight is Length1 and Length3. The equation is Weight= -1675.79 + -105.64 * Length1 + 141.25 * Length3.


The best model using two variables to predict Roach weight is Length3 and Width. The equation is Weight= -319.118 + 8.278 * Length3 + 72.300 * Width.


